---
title: "Word document Preliminary Analysis"
author: "Yasmin Roustaei"
date: "18 May 2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup,echo=FALSE}
library(readxl)
Lizard_data<-read_excel("~/Lizard data.xlsx")

```

```{r}
getwd()
```
[1] We hypothesise that allelic richness of Eulamprus leuraensis populations will 
increase with increasing elevation. We hypothesise that expected heterozygosity and observed heterozygosity of 
Eulamprus leuraensis populations will increase with increasing elevation. 

[2] Dependent variables-allelic richness, observe heterozygosity, and expected heterozygosity.
Independent variables-elevation (500, 600, 700, 800, 900, 1000, 1100 metres). 

[3] A linear regression will be used to assess the relationship between elevation and genetic 
diversity (allelic richness, observed heterozygosity, and expected heterozygosity). The 
statistical null hypothesis is that the linear relationship between Y (allelic richness, observed 
heterozygosity, and expected heterozygosity) is equal to 0. The alternative hypothesis is that 
the linear relationship between Y (allelic richness, observed heterozygosity, and expected 
heterozygosity) is not equal to 0. 

[4] Independence of data within and among samples, X variable is measured without error, 
Normality of the residuals about the fitted line, m X + b, Homogeneity of variances for 
residuals about the fitted line m X + b, and Linear relationship

[5]Results
The plot illustrates a linear relationship. This suggests that the assumption the relationship is 
linear is reasonable. It also suggests that there are no unusual data points. It also illustrates 
that the variation around the estimated regression line is constant suggesting that the 
assumption of equal variances is reasonable. Assumption of normality also seems reasonable 
as values follow a reasonably straight line (Figure 2).

There is a significant relationship between the elevation of the mountain and allelic richness 
(AR) (Linear regression: Df=1,12, R2=0.59, P=0.0022). Allelic richness increased with 
increasing elevation (Figure 1). There is also a significant relationship between the elevation 
and expected heterozygosity (Hs) (Linear regression: Df=1,12, R2=0.54, P=0.0043). Expected 
heterozygosity increased with increasing elevation. Therefore, I reject the null hypothesis that 
the linear relationship between allelic richness and expected heterozygosity is equal to 0. 


```{r plot1, echo=FALSE}
plot(Lizard_data$Elevation,Lizard_data$AR, xlab='Elevation',ylab='AR',main='Relationship between Elevation and AR',col='blue')

```

```{r}
getwd()
```
Figure 1: Relationship between mountain elevation and allelic richness (AR)



```{r plot2,echo=FALSE}
qqnorm(Lizard_data$AR)
qqline(Lizard_data$AR)

```

``` {r}
getwd()
```
Figure 2: Normal qqplot for residuals

```{r}
getwd()
```
Table 1: Elevation of population sites and number of lizard tail samples collected per each 
population (N), observed heterozygosity (Ho), expected heterozygosity (Hs), and allelic 
richness (AR).
Observed heterozygosity (Ho), expected heterozygosity (Hs), and allelic richness (AR) of 
Eulamprus leuraensis populations was higher at higher elevations compared to lower 
elevations sites (Table 1). 

```{r plot3, echo=FALSE}
summary(Lizard_data)
